On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-22 ms-suppinfo.Rnw
clarify list of outsanding issues, including in the theoretical sections

For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator. For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

@@

\noindent\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ). Fig. \ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).

@@

The temporal changes were confounded with a plant stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions. The conclusions of a meta-analysis conducted in different years should not differ from those reported here.

>>>>

For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

@@

\noindent\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ). Fig. \ref{fig:figA9} shows that for these three traits the publication years may be confounded with ontogenetic stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).

@@

The temporal changes were confounded with a ontogenetic stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions. The conclusions of a meta-analysis conducted in different years should not differ from those reported here.

### 2016-01-22 ms-suppinfo.tex
clarify list of outsanding issues, including in the theoretical sections

For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator. For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

>>>>

For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
